\thetitle

### 2020-11-21 writing/sample.tex
sample: small rewording

In summary, our sampling process takes advantage of ancillary information
to deliver a  sufficiently large representative set of scenarios.
Concretely, we test each
mode of the rational programmer on 72,192 randomly selected interesting
debugging scenarios spread across both benchmarks and mutators.
Furthermore stratified random sampling allows us to derive precise conclusions
about the proportion of the whole population that satisfies a given trait 
from the proportion of the sample 
that satisfies the trait despite the population's heterogeneity, exactly what we need to project comparisons about the
usefulness of various modes of the
rational programmer from the sample to the set of all interesting debugging
scenarios.

>>>>

In summary, our sampling process takes advantage of ancillary information
to deliver a  sufficiently large representative set of scenarios.
Concretely, we test each
mode of the rational programmer on 72,192 randomly selected interesting
debugging scenarios spread across both benchmarks and mutators.
Furthermore, stratified random sampling allows us to derive precise conclusions
about the proportion of the whole population that satisfies a given trait 
from the sample despite the population's heterogeneity.
That property is exactly what we need to project comparisons about the
usefulness of various modes of the
rational programmer from the sample to the set of all interesting debugging
scenarios.
